---
title: "RThesis"
author: "Hyungbin Park"
date: "4/19/2020"
output: html_document
---

```{r}
setwd("~/Downloads")
library(readr)
```

# 2017 Noise and Heat Call DATA
```{r}
#Reading noise and heating calls in 2017 and reducing the columns
noise17 <- read_csv("noise17orig.csv")
noise2017 <- noise17[c("Unique Key", "Latitude", "Longitude")]
write_csv(noise2017, path = "Noise2017.csv")
heat17 <- read_csv("heat17orig.csv")
heat2017 <- heat17[c("Unique Key", "Latitude", "Longitude")]
write_csv(heat2017, path = "Heat2017.csv")

#loading the joined layer made with QGIS and aggregating the calls by NTA
no17 <- read_csv("no17.csv")
no17
no17new <- aggregate(no17$"Unique Key", by=list(no17$NTACode), FUN=length)
no17new
names(no17new) <- c("NTACode","CallCount")
sum(no17new$CallCount)

ht17 <- read_csv("ht17.csv")
View(ht17)
ht17new <- aggregate(ht17$"Unique Key", by=list(ht17$NTACode), FUN=length)
ht17new
names(ht17new) <- c("NTACode","CallCount")
sum(ht17new$CallCount)

noise_heat_17 <-merge(no17new, ht17new, by.x = "NTACode",by.y = "NTACode", all.x = TRUE)
names(noise_heat_17) <- c("NTACode","Noise Call Count", "Heat Call Count")
write_csv(noise_heat_17, path="noise_heat_17.csv")
```

# 2013 Noise and Heat Call DATA
```{r}
#Reading noise and heating calls in 2013 and reducing the columns
noise13 <- read_csv("noise13orig.csv")
noise2013 <- noise13[c("Unique Key", "Latitude", "Longitude")]
write_csv(noise2013, path = "Noise2013.csv")
heat13 <- read_csv("heat13orig.csv")
heat2013 <- heat13[c("Unique Key", "Latitude", "Longitude")]
write_csv(heat2013, path = "Heat2013.csv")

#loading the joined layer made with QGIS and aggregating the calls by NTA
no13 <- read_csv("no13.csv")
View(no13)
no13new <- aggregate(no13$"Unique Key", by=list(no13$NTACode), FUN=length)
View(no13new)
names(no13new) <- c("NTACode","CallCount")
sum(no13new$CallCount)

ht13 <- read_csv("ht13.csv")
View(ht13)
ht13new <- aggregate(ht13$"Unique Key", by=list(ht13$NTACode), FUN=length)
names(ht13new) <- c("NTACode","CallCount")
View(ht13new)
sum(ht13new$CallCount)

noise_heat_13 <-merge(no13new, ht13new, by.x = "NTACode",by.y = "NTACode", all.x = TRUE, all.y = TRUE)
names(noise_heat_13) <- c("NTACode","Noise Call Count", "Heat Call Count")
View(noise_heat_13)
write_csv(noise_heat_13, path="noise_heat_13.csv")
```

# 2015 Noise and Heat Call DATA
```{r}
#Reading noise and heating calls in 2015 and reducing the columns

noise15 <- read_csv("noise15orig.csv")
noise2015 <- noise15[c("Unique Key", "Latitude", "Longitude")]
write_csv(noise2015, path = "Noise2015.csv")
View(noise2015)
heat15 <- read_csv("heat15orig.csv")
heat2015 <- heat15[c("Unique Key", "Latitude", "Longitude")]
write_csv(heat2015, path = "Heat2015.csv")

#loading the joined layer made with QGIS and aggregating the calls by NTA
no15 <- read_csv("no15.csv")
no15
no15new <- aggregate(no15$"Unique Key", by=list(no15$NTACode), FUN=length)
no15new
names(no15new) <- c("NTACode","CallCount")
sum(no15new$CallCount)

ht15 <- read_csv("ht15.csv")
View(ht15)
ht15new <- aggregate(ht15$"Unique Key", by=list(ht15$NTACode), FUN=length)
ht15new
names(ht15new) <- c("NTACode","CallCount")
sum(ht15new$CallCount)

noise_heat_15 <-merge(no15new, ht15new, by.x = "NTACode",by.y = "NTACode", all.x = TRUE, all.y = TRUE)
names(noise_heat_15) <- c("NTACode","Noise Call Count", "Heat Call Count")
write_csv(noise_heat_15, path="noise_heat_15.csv")
```


```{r}
# Importing the gini and total population by tract from ACS 
ginitract2013 <- read_csv("ginitract2013.csv")
ginitract2013 <- ginitract2013[-c(1),]
tptract2013 <- read_csv("tptract2013.csv")
tptract2013 <- tptract2013[-c(1),]
ginitract2015 <- read_csv("ginitract2015.csv")
ginitract2015 <- ginitract2015[-c(1),]
tptract2015 <- read_csv("tptract2015.csv")
tptract2015 <- tptract2015[-c(1),]

# Merging gini and total population by tract 
tract2013 <-merge(ginitract2013, tptract2013, by.x = "GEO_ID",by.y = "GEO_ID", all.x = TRUE)
tract2013 <- tract2013[c(1,2,3,6)]
tract2013$tract_id <- substring(tract2013[,1],15,20)
tract2013$boro_id <- substring(tract2013[,1],12,14)
tract2013$tractboro <- substring(tract2013[,1],12,20)
tract2013 <- tract2013[c(2,7,6,5,3,4)]
View(tract2013)

tract2015 <-merge(ginitract2015, tptract2015, by.x = "GEO_ID",by.y = "GEO_ID", all.x = TRUE)
tract2015 <- tract2015[c(1,2,3,6)]
tract2015$tract_id <- substring(tract2015[,1],15,20)
tract2015$boro_id <- substring(tract2015[,1],12,14)
tract2015$tractboro <- substring(tract2015[,1],12,20)
tract2015 <- tract2015[c(2,7,6,5,3,4)]
View(tract2015)
```

#importing nta_tract equivalent map data
```{r}
tract_nta <- read_csv("tract_nta.csv")
tract_nta$tractboro <- paste(tract_nta$County, tract_nta$Tract, sep="")
tract_nta <- tract_nta[c(3,1,2)]
```

#merging the nta_tract equivalent data with the gini and total population data 
```{r}
tractnta2013 <-merge(tract2013, tract_nta, by.x = "tractboro",by.y = "tractboro", all.x = TRUE)
tractnta2013 <- tractnta2013[c(1,5,6,7,8)]
tractnta2013 <- tractnta2013[order(tractnta2013$NTAName),]
row.names(tractnta2013) <- NULL
names(tractnta2013)[2] <- "gini"
names(tractnta2013)[3] <- "population"
View(tractnta2013)
tractnta2015 <-merge(tract2015, tract_nta, by.x = "tractboro",by.y = "tractboro", all.x = TRUE)
tractnta2015 <- tractnta2015[c(1,5,6,7,8)]
tractnta2015 <- tractnta2015[order(tractnta2015$NTAName),]
row.names(tractnta2015) <- NULL
names(tractnta2015)[2] <- "gini"
names(tractnta2015)[3] <- "population"
View(tractnta2015)

write_csv(tractnta2013, path = "tractnta2013.csv")
write_csv(tractnta2015, path = "tractnta2015.csv")
```

#importing queried tables of weighted gini by NTA
```{r}
weighted2013 <- read_csv("weighted2013.csv")
View(weighted2013)
weighted2015 <- read_csv("weighted2015.csv")
View(weighted2015)
```

# Merging the weighted gini and noise heat calls in 2013 and 2015
```{r}
nohtgini13 <-merge(weighted2013, noise_heat_13, by.x = "NTACode",by.y = "NTACode", all.x = TRUE, all.y = TRUE)
View(nohtgini13)
write_csv(nohtgini13, path = "nohtgini13.csv")
nohtgini15 <-merge(weighted2015, noise_heat_15, by.x = "NTACode",by.y = "NTACode", all.x = TRUE, all.y = TRUE)
View(nohtgini15)
write_csv(nohtgini15, path = "nohtgini15.csv")
```

##Importing and merging the data files and finalizing the dataset for 2017
```{r}
noht17 <- read_csv("noise_heat_17.csv")
gicen17 <- read_csv("ginicensus2017.csv")

final17 <-merge(gicen17, noht17, by.x = "NTACode",by.y = "NTACode", all.x = TRUE)
View(final17)
final17 <- final17[-c(196,197,198),]
final17["r_ncall"] <- (final17$`Noise Call Count`)/ (final17$Pop_1E)
final17["r_hcall"] <- (final17$`Heat Call Count` )/ (final17$Pop_1E)
final17["lr_ncall"] <- log((final17$`Noise Call Count`)/ (final17$Pop_1E))
final17["lr_hcall"] <- log((final17$`Heat Call Count` )/ (final17$Pop_1E))
write_csv(final17, path = "final17.csv")
colnames(final17)
```

##Importing and merging the data files and finalizing the dataset for 2013
```{r}
nohtgini13 <- read_csv("nohtgini13.csv")
View(nohtgini13)
census13 <- read_csv("census13.csv")
census13 <- census13[-c(196,197),]
View(census13)

final13 <-merge(census13, nohtgini13, by.x = "GeoID",by.y = "NTACode", all.x = TRUE)
View(final13)
final13["r_ncall"] <- (final13$`Noise Call Count`)/ (final13$PopE)
final13["r_hcall"] <- (final13$`Heat Call Count` )/ (final13$PopE)
final13["lr_ncall"] <- log((final13$`Noise Call Count`)/ (final13$PopE))
final13["lr_hcall"] <- log((final13$`Heat Call Count` )/ (final13$PopE))
write_csv(final13, path = "final13.csv")
colnames(final13)
```

##Importing and merging the data files and finalizing the dataset for 2015
```{r}
nohtgini15 <- read_csv("nohtgini15.csv")
View(nohtgini15)
census15 <- read_csv("census15.csv")
census15 <- census15[-c(196,197),]
View(census15)

final15 <-merge(census15, nohtgini15, by.x = "GeoID",by.y = "NTACode", all.x = TRUE)
View(final15)
final15["r_ncall"] <- (final15$`Noise Call Count`)/ (final15$Pop_1E)
final15["r_hcall"] <- (final15$`Heat Call Count` )/ (final15$Pop_1E)
final15["lr_ncall"] <- log((final15$`Noise Call Count`)/ (final15$Pop_1E))
final15["lr_hcall"] <- log((final15$`Heat Call Count` )/ (final15$Pop_1E))
write_csv(final15, path = "final15.csv")
colnames(final15)
```

# renaming the columns for the finalized dataset 2013, 2015, 2017
```{r}
dim(final13)
dim(final15)
dim(final17)
colnames(final13)
colnames(final15)
colnames(final17)

final15 <- final15[c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,18,16,17,19,20,21,22,23,24,25)]
final17 <- final17[c(1,2,4,5,6,7,8,9,10,11,12,13,14,15,19,16,17,18,3,20,21,22,23,24,25)]
names(final13) <- c("NTACode","NTAName","population","malep","hispanicp","whitep","blackp","asianp",
                    "lessthanHSp","morethanBAp","samehousep","foreignbornp","younger18p","older65p",
                    "medianincome","medianrent","rentvacrate","renteroccup","gini","noisecallcount",
                    "heatcallcount","noisecallrate","heatcallrate","lognoiserate","logheatrate")
names(final15) <- c("NTACode","NTAName","population","malep","hispanicp","whitep","blackp","asianp",
                    "lessthanHSp","morethanBAp","samehousep","foreignbornp","younger18p","older65p",
                    "medianincome","medianrent","rentvacrate","renteroccup","gini","noisecallcount",
                    "heatcallcount","noisecallrate","heatcallrate","lognoiserate","logheatrate")
names(final17) <- c("NTACode","NTAName","population","malep","hispanicp","whitep","blackp","asianp",
                    "lessthanHSp","morethanBAp","samehousep","foreignbornp","younger18p","older65p",
                    "medianincome","medianrent","rentvacrate","renteroccup","gini","noisecallcount",
                    "heatcallcount","noisecallrate","heatcallrate","lognoiserate","logheatrate")

```

# adding a year variable and merging vertically the 3 final data together
```{r}
final13$year <- "2013"
final15$year <- "2015"
final17$year <- "2017"
finalvertical <- rbind(final13, final15, final17)
finalvertical <- finalvertical[c(26,1:25)]

# excluding the cemeteries in 5 boroughs, airport and rikers island
finalvertical <- finalvertical[!(finalvertical$NTACode == "MN99"|finalvertical$NTACode =="BK99"|finalvertical$NTACode =="BX99"|finalvertical$NTACode =="SI99"|finalvertical$NTACode =="QN99"|finalvertical$NTACode =="BX98"|finalvertical$NTACode =="QN98"),]

dim(finalvertical)
View(finalvertical)
write_csv(finalvertical, path = "finalvertical.csv")
```

